\documentclass[12pt]{article}
\usepackage{fancyhdr}
\usepackage{amsmath}
\usepackage{amssymb, amsmath, graphicx,amsthm,setspace}
\pagestyle{fancy}

\lhead[lh-even]{\textbf{Michael Vu}}  
\lfoot[lf-even]{} 
\chead[ch-even]{\textbf{2.3 Theorem}}  
\cfoot[cf-even]{} 
\rhead[rh-even]{September 26, 2017}  
\rfoot[rf-even]{}

\begin{document}
\noindent\textbf{Lemma TP.} Let $a,b,c\in\mathbb{Z}$. If $a|b$ and $b|c$, then $a|c$.

\bigskip

\noindent\textbf{Proof.} Let $a,b,c\in\mathbb{Z}$ be given such that $a|b$ and $b|c$. By definition, $b=ax$ and $c=by$ for some $x,y\in\mathbb{Z}$. Substituting into $c$,

\begin{align*}
c &= (ax)y \\
&= a(xy).
\end{align*}

\noindent By CPI, $xy=t$ for $t\in\mathbb{Z}$. Thus, $a|c$.\qed

\bigskip

\noindent\textbf{2.3 Theorem.} A natural number $n>1$ is prime if and only if for all primes $p\leq \sqrt{n}$, $p$ does not divide $n$.

\bigskip

\noindent\textbf{Proof.} Let a natural number $n>1$ be given. Suppose $n$ is prime, then $p\not| n$ for all primes $p\leq \sqrt{n}$. Suppose not. That is, let $n$ be prime, and that there exists a prime $p\leq \sqrt{n}$ such that $p|n$. Since $n$ is prime, by definition on page 29 of our text, we can conclude only $1|n$ and $n|n$. Observe that $p\leq\sqrt{n}<n$. This leads us to conclude $p=1$, since $p|n$. 1 is not a prime number, this contradicts $p$ being prime. Thus, there does not exist $p$ and $p\not| n$.

\bigskip

\noindent Now we will show if $p\not| n$ for all primes $p\leq \sqrt{n}$, then $n$ is prime. We will prove by contrapositive. That is, suppose $n$ is composite, there exists a prime $p\leq \sqrt{n}$ such that $p|n$. Since $n$ is composite, let $n=dn'$ for some $d,n'\in\mathbb{Z}$ with $1<d\leq n'$. Thus,

\begin{align*}
d^2 &\leq dn' = n, \\
d^2 &\leq n, \\
d &\leq \sqrt{n}.
\end{align*}

\noindent Since $d>1$, by Theorem 2.1, $p|d$. Since $d|n$, by Lemma TP, $p|n$. Thus, $n$ is prime since our contrapositive is true.

\bigskip

\noindent Now that we have shown both directions of the biconditional statement to be true, $n$ is prime if and only if $p\not| n$, for all primes $p\leq \sqrt{n}$.\qed

\end{document}